An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
clarification about screenshot
spelling corrections

Recent years have seen an explosion of online services for learning
to program:  Udacity\cite{udacity}, Codecademy\cite{codeacademy},
ProgZoo\cite{progzoo}, 
Codingbat\cite{codingbat}, Coursera\cite{coursera}, CodeLab\cite{turingscraft},
Problets\cite{Kumar:2005:GPA:1163405.1163408}, CS Circles\cite{Pritchard:2013:CCI:2445196.2445370} and
many others.  These systems are powerful, and show great promise to
improve introductory computer science.  Given the existence of all of these
systems, one may ask why we thought
%it a good career move
%to build yet another system.
the world needed another such system.

@@

Figure~\ref{screenshot} shows a screenshot of a CloudCoder exercise.
CloudCoder uses Ace\cite{ace}, an open source web-based
programmer's editor, which supports
syntax highlighting and automatic indentation for most programming languages.
The submit button runs the code against a series of
test cases. Once the test results are received, they are presented
directly in the browser, giving the student immediate feedback on the
correctness of the submission.
CloudCoder captures the code's standard output and
standard error streams to help students with debugging.

@@

CloudCoder is available under the GNU Affero General Public License\cite{AGPL}.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on Github:
\begin{quote}
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\end{quote}

@@

Whole-program exercises read input data from
the standard input stream, perform a computation, and write output to the standard output stream.
Expected output is checked by matching a regular expression against the
program's standard output stream.
Whole-program exercises are useful for two main reasons.  First,
they can be assigned early in the course, before functions/methods
have been introduced.  Second, they give the exercise author a
way of checking expected output that is more powerful than matching a return
value against a literal.  The main disadvantage is
the difficulty of devising a
regular expression that is precise enough to distinguish correct output
from incorrect output, but forgiving enough to allow minor deviations
in whitespace, capitalization, and formatting of output.

@@

\section{Acknowledgements}

>>>>

Recent years have seen an explosion of online services for learning
to program:  Udacity\cite{udacity}, Codecademy\cite{codeacademy},
ProgZoo\cite{progzoo}, 
CodingBat\cite{codingbat}, Coursera\cite{coursera}, CodeLab\cite{turingscraft},
Problets\cite{Kumar:2005:GPA:1163405.1163408}, CS Circles\cite{Pritchard:2013:CCI:2445196.2445370} and
many others.  These systems are powerful, and show great promise to
improve introductory computer science.  Given the existence of all of these
systems, one may ask why we thought
%it a good career move
%to build yet another system.
the world needed another such system.

@@

Figure~\ref{screenshot} shows a screenshot of the user interface
students use to work on a CloudCoder exercise.
CloudCoder uses Ace\cite{ace}, an open source web-based
programmer's editor, which supports
syntax highlighting and automatic indentation for most programming languages.
The submit button runs the code against a series of
test cases. Once the test results are received, they are presented
directly in the browser, giving the student immediate feedback on the
correctness of the submission.
CloudCoder captures the code's standard output and
standard error streams to help students with debugging.

@@

CloudCoder is available under the GNU Affero General Public License\cite{AGPL}.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on GitHub:
\begin{quote}
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\end{quote}

@@

Whole-program exercises read input data from
the standard input stream, perform a computation, and write output to the standard output stream.
Expected output is checked by matching a regular expression against the
program's standard output stream.
Whole-program exercises are useful for two main reasons.  First,
they can be assigned early in the course, before functions/methods
have been introduced.  Second, they give the exercise author a
way of checking expected output that is more powerful than matching a return
value against a literal.  The main disadvantage is
the difficulty of devising a
regular expression that is precise enough to distinguish correct output
from incorrect output, but forgiving enough to allow minor deviations
in white space, capitalization, and formatting of output.

@@

\section{Acknowledgments}
